---
title: "Chloroquine concentration-fatality curve"
author: "James Watson"
date: "4/20/2020"
output:
  html_document:
    df_print: paged
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, cache.comments = FALSE, 
                      include = TRUE, echo = TRUE, 
                      fig.width = 9, fig.height = 9,
                      fig.pos = 'H', 
                      dev = 'png', dpi = 300)
library(knitr)
library(gtools)
library(rstan)
library(RColorBrewer)
RUN_MODELS=F

#****** Parameters for the analysis *******
plasma_to_whole_blood_ratio = 3 # conversion for PK model 2
Weight_interested = 70 # displays results for chosen weight - has to be multiple of 5 between 40 and 90!

```

## Data from self-poisoning cohorts

Data from Riou were extracted from published graph (see Figure 3 in NEJM Riou et al, 1988) using WebPlotDigitiser

```{r pooled_data}
pooled_data = read.csv('Pooled_data.csv')
```

#### Comparing retrospective and prospective dat

We use simple logistic regression on admission concentrations to demonstrate significant differences between the retrospective and prospective data
```{r retro_vs_pros}
par(las=1, family='serif', bty='n')
ind_pros = pooled_data$Prospective=='Yes'
mod_pros = glm(Outcome ~ log(CQumolL_Admission), data = pooled_data[ind_pros,], family='binomial')
mod_retro = glm(Outcome ~ log(CQumolL_Admission), data = pooled_data[!ind_pros,], family='binomial')
summary(mod_pros)
summary(mod_retro)
coef(mod_pros)
coef(mod_retro)

plot(1:100, predict(mod_pros, newdata = data.frame(CQumolL_Admission=1:100),type='response'),type='l',
     ylim=c(0,1),lwd=3, xlab='Chloroquine concentration (umol/L)',
      ylab='Probability of death', panel.first=grid())
lines(1:100, predict(mod_retro, newdata = data.frame(CQumolL_Admission=1:100),type='response'),
      col='blue',lwd=3,lty=2)
legend('bottomright', lwd=3, legend = c('Prospective data','Retrospective data'),col=c(1,4),
       inset=0.03, lty=1:2)
```

```{r}
# ind_clemessy=pooled_data$Study=='Clemessy'
# ind_mb = pooled_data$Study=='Megarbane'
# 
# mod_1 = glm(Outcome ~ log(CQumolL_Admission), data = pooled_data[ind_clemessy,], family='binomial')
# mod_2 = glm(Outcome ~ log(CQumolL_Admission), data = pooled_data[ind_mb,], family='binomial')
# 
# plot(1:100, predict(mod_1, newdata = data.frame(CQumolL_Admission=1:100),type='response'),type='l',
#      ylim=c(0,1),lwd=3, xlab='Chloroquine concentration (umol/L)',
#       ylab='Probability of death', panel.first=grid())
# lines(1:100, predict(mod_2, newdata = data.frame(CQumolL_Admission=1:100),type='response'),
#       col='blue',lwd=3,lty=2)
# legend('bottomright', lwd=3, legend = c('Prospective data','Retrospective data'),col=c(1,4),
#        inset=0.03, lty=1:2)

```



#### Estimating delta increase in those with observed peak

We only use prospectively studied patients - the retrospectively studied patients have quite a different concentration-fatality profile.

```{r}
pooled_data = dplyr::filter(pooled_data, Prospective=='Yes')
ind_increase = which(!is.na(pooled_data$CQumolL_Peak) &
                       pooled_data$CQumolL_Peak>pooled_data$CQumolL_Admission)
writeLines(sprintf('%s patients had their peak observed in hospital', length(ind_increase)))
hist(log10(pooled_data$CQumolL_Peak[ind_increase])-
       log10(pooled_data$CQumolL_Admission[ind_increase]), main='', 
     xlab='delta: increase in log concentration in those who peaked at hospital')
```

## Stan model

```{r}
logistic_model = '
data {
   int<lower=0> N_admission;
   int<lower=0> N_peak;
   vector[N_admission] log_conc_admission;
   vector[N_peak] log_conc_peak;
   int<lower=0,upper=1> y_admission[N_admission];
   int<lower=0,upper=1> y_peak[N_peak];
   // Prior parameters
   real mean_alpha;
   real sd_alpha;
   real mean_beta;
   real sd_beta;
}
parameters {
   real alpha; // Intercept term in logistic regression
   real beta;  // Concentration coefficient in logistic regression
   real<lower=0> delta; // Mean increase in chloroquine concentrations on the log scale
   real<lower=0,upper=1> gamma; // Fraction of chloroquine in measured concentration
}
model {
  //Prior
  alpha ~ normal(mean_alpha,sd_alpha);
  beta ~ normal(mean_beta,sd_beta);
  gamma ~ normal(0.7, 0.065); // Prior is estimated from a large CQ&DCQ dataset
  delta ~ exponential(7.8); // rate parameter estimated from the observed peak vs admission
  // Likelihood
  y_peak ~ bernoulli_logit(alpha + beta * (log(0.7 * (exp(log_conc_peak)))));
  y_admission ~ bernoulli_logit(alpha + beta * (log(0.7 * (exp(log_conc_admission))) + delta));
}
'
if(RUN_MODELS) log_reg = stan_model(model_code = logistic_model)
```

## Fit main model to prospective data

```{r, include=FALSE}
N_iter = 10^4
N_thin = 14
N_chains = 4
#options(mc.cores = N_chains)
prior_params = list(mean_alpha = -15, sd_alpha=1, mean_beta=4, sd_beta=1)

ind_increase = !is.na(pooled_data$CQumolL_Peak) & pooled_data$CQumolL_Peak>pooled_data$CQumolL_Admission
CQ_data = list(N_admission = as.integer(sum(!ind_increase)),
               N_peak = as.integer(sum(ind_increase)),
               log_conc_admission = log(pooled_data$CQumolL_Admission[!ind_increase]),
               log_conc_peak = log(pooled_data$CQumolL_Peak[ind_increase]),
               y_admission = as.integer(pooled_data$Outcome[!ind_increase]),
               y_peak = as.integer(pooled_data$Outcome[ind_increase]))

if(RUN_MODELS){
  mod_full = sampling(log_reg,
                      data=c(CQ_data, prior_params),
                      iter = N_iter, thin = N_thin, chains= N_chains)
  
  save(mod_full, file = 'mod_full.stanout')
}
```


```{r priors_vs_posteriors}
load('mod_full.stanout')
thetas = extract(mod_full)
par(mfrow=c(2,2),las=1, cex.lab=1.5)
hist(thetas$alpha, freq = F,breaks = 50,main = '', xlab = expression(alpha), col = 'grey',
     ylab='', yaxt='n')
xs = seq(min(thetas$alpha), max(thetas$alpha), length.out=500)
lines(xs, dnorm(xs, mean = prior_params$mean_alpha, sd = prior_params$sd_alpha), lwd=3, col='red')
hist(thetas$beta,freq=F,breaks = 50,main = '', xlab = expression(beta), col = 'grey',
     ylab='', yaxt='n')
xs = seq(min(thetas$beta), max(thetas$beta), length.out=500)
lines(xs, dnorm(xs, mean = prior_params$mean_beta, sd = prior_params$sd_beta), lwd=3, col='red')

hist(thetas$delta, freq=F,breaks = 50,main = '', xlab = expression(delta), col = 'grey',
     ylab='', yaxt='n')
xs=seq(0,2,length.out = 2000); lines(xs, dexp(xs,rate=7.8),col='red',lwd=3)

hist(thetas$gamma, freq=F,breaks = 50,main = '', xlab = expression(gamma), col = 'grey',
     ylab='', yaxt='n')
xs=seq(0,1,length.out = 500); lines(xs, dnorm(xs,mean=0.7, sd=0.065),col='red',lwd=3)
```


```{r one_percent_mortality}
K = length(thetas$alpha)
OnePercent = array(dim=K)
xs = seq(0, log(100), length.out = 200)
Pred_mortality = array(dim=c(K, 200))
for(k in 1:K){
  OnePercent[k] = exp((logit(0.01) - thetas$alpha[k])/thetas$beta[k])
  Pred_mortality[k, ] = inv.logit(thetas$alpha[k] + thetas$beta[k] * xs)
}

plot(density(OnePercent),xlab='Chloroquine concentration in whole blood (umol/L)', 
     main = 'Concentration that gives 1% mortality', yaxt='n', ylab='', bty='n',lwd=3)
abline(v=quantile(OnePercent, probs = c(0.025, 0.975)),lty=2)
print(quantile(OnePercent, probs = c(0.025, 0.5, 0.975)))
```

# Pharmacokinetic models output

```{r compare_PK_models}
load('Population_Cmax_values.RData')

# plasma model
ind_plasma = grep(pattern = 'plasma', x = unlist(dimnames(Cmax_pop)[1]))
# whole blood model
ind_WB = grep(pattern = 'WB', x = unlist(dimnames(Cmax_pop)[1]))
Cmax_pop[ind_plasma,,,] = Cmax_pop[ind_plasma,,,]*plasma_to_whole_blood_ratio
cols = brewer.pal(8, name = 'Dark2')[c(6,4,7,8)]
cols = c(cols[1], cols[2], cols[3],cols[1],cols[3],cols[4])
cols=c(cols,cols)
cnames = unlist(dimnames(Cmax_pop)[1])

legend_names = c('310mg twice daily (10 days)','600mg twice daily (10 days)',
                 '310mg twice daily (7 days)', 
                 'Weight-based (10 days)','Weight-based (7 days)',
                 'Malaria treatment (3 days)')

par(mfrow=c(2,3),bty='n',las=1, family='serif')
ws = grep(pattern = Weight_interested, x = unlist(dimnames(Cmax_pop)[2]))
for(i in 1:length(ind_plasma)){
  plot(density(Cmax_pop[ind_plasma[i],ws,,1]), main=legend_names[i], ylim=c(0,0.6),
       xlab=expression(mu*'mol/L'), ylab='', yaxt='n', xlim=c(0,20),lwd=3)
  lines(density(Cmax_pop[ind_WB[i],ws,,1]),col='red',lwd=3)
  writeLines(sprintf('Median cmax for regimen %s is %s under whole blood model and %s under plasma model',
                     cnames[i], round(median(Cmax_pop[ind_WB[i],ws,,1]),1),
                     round(median(Cmax_pop[ind_plasma[i],ws,,1],1))))
}
legend('topright',title = paste('Cmax in',Weight_interested,'kg adult'), col=2:1, 
       lwd=3, legend = c('Whole blood','Plasma'))
for(i in 1:length(ind_plasma)){
  qqplot(Cmax_pop[ind_WB[i],ws,,1], Cmax_pop[ind_plasma[i],ws,,1], main=cnames[i], 
         xlab='Whole blood model', ylab='Plasma model', pch='.')
  lines(0:100,0:100)
}

median_cmax = array(dim = c(dim(Cmax_pop)[1], dim(Cmax_pop)[2]))
for(i in 1:dim(Cmax_pop)[1]){
  for(j in 1:dim(Cmax_pop)[2]){
    median_cmax[i,j] = median(Cmax_pop[i,j,,1])
  }
}
par(mfrow=c(1,1),bty='n',las=1, family='serif')
plot(seq(40,90, by=5), median_cmax[1,],type='l', ylim=range(median_cmax),xlab='weight', ylab='Median Cmax')
for(i in 2:dim(Cmax_pop)[1]){
  if(i > 6) lwds=3 else lwds = 1
  lines(seq(40,90, by=5), median_cmax[i,], col=cols[i],lwd=lwds)
}
```




```{r}
q = 1
uCI_mortality_per_thousand = 
  lCI_mortality_per_thousand = 
  mean_mortality_per_thousand = 
  above_threshold = array(dim = c(dim(Cmax_pop)[1], 11))

colnames(uCI_mortality_per_thousand)=
  colnames(lCI_mortality_per_thousand)=
  colnames(mean_mortality_per_thousand)=
  colnames(above_threshold)= unlist(dimnames(Cmax_pop)[2])
rownames(uCI_mortality_per_thousand)=
  rownames(lCI_mortality_per_thousand)=
  rownames(mean_mortality_per_thousand)=
  rownames(above_threshold)= unlist(dimnames(Cmax_pop)[1])

for(i in 1:dim(Cmax_pop)[1]){
  Cmax_pop_fs = Cmax_pop[i,,,q]
  above_one_percent = ps = array(dim=c(11,K))
  
  for(w in 1:11){
    for(k in 1:K){
      cqs = Cmax_pop_fs[w,]
      cqs = cqs[!is.na(cqs)]
      
      danger_threshold = exp((logit(0.01)-thetas$alpha[k])/thetas$beta[k])
      ind_above = cqs > danger_threshold
      above_one_percent[w,k] = mean(ind_above)
      
      if(mean(ind_above)>0){
        mean_mortality = mean(inv.logit(thetas$alpha[k] + 
                                          thetas$beta[k]*log(cqs[ind_above])), na.rm=T)
        ps[w,k] = mean_mortality * mean(ind_above)
      } else {
        ps[w,k] = 0
      }
    }
  }
  above_threshold[i, ] = rowMeans(above_one_percent)*100
  mean_mortality_per_thousand[i,] = rowMeans(ps)*1000
  uCI_mortality_per_thousand[i,] = apply(ps,1,quantile,probs=0.975)*1000
  lCI_mortality_per_thousand[i,] = apply(ps,1,quantile,probs=0.025)*1000
}
```


Hoglund et al malaria patient whole blood model: predictions for Cmax greater than threshold and per thousand mortality
```{r Fig2, fig.width=10, fig.height=9}
# Set the indices to the simulations from the whole blood model
ind_model = ind_WB

ltys = rep(c(1,1,1,2,2,1),2)
lwds = c(rep(3,6), rep(2,6))
tick_points = c(1:19,seq(20,100,by=10))
x_points = c(2,3,5,10,13,20)

par(las=1, bty='n', family = 'serif',cex.lab=1.5, cex.axis=1.5,mar=c(5,6,2,2))
layout(mat = matrix(c(1,1,2,3), nrow = 2, byrow = T))

plot(density(log(Cmax_pop[ind_model[1],ws,,q]),na.rm=T), xlim = log(c(2, 20)),ylab='',yaxt='n', 
     xaxt='n', main='',col=cols[ind_model[1]],lwd=lwds[ind_model[1]], ylim=c(0,2.2),
     xlab = expression(paste('Whole blood chloroquine concentration (',mu,'mol/L)')))
for(i in ind_model[-1]){
  lines(density(log(Cmax_pop[i,ws,,q]),na.rm=T), lwd=lwds[i],col=cols[i],lty=ltys[i])
}
axis(1, at=log(x_points),labels = x_points)
axis(1, at = log(tick_points), labels = NA, tick = T)
legend('topleft',legend = legend_names,bg = 'white',col=cols[ind_model],
       lwd=2,inset=0.02,lty=ltys[ind_model],
       title = paste('Cmax for', Weight_interested,'kg adult'))
qs=quantile(OnePercent, probs = c(0.025,0.975))
polygon(x = log(c(qs,rev(qs))), y = c(-9,-9,10,10), 
        col = adjustcolor('red',alpha.f = .2),border = NA)
mtext(text = 'A',side = 3,cex=1.5,adj = 0)

## Probability of being above threshold
plot(seq(40,90,by=5), log10(above_threshold[ind_model[1], ]/100), type='l',main='',
     ylim=c(-3,0),col=cols[ind_model[1]],lwd=lwds[ind_model[1]],
     panel.first = grid(), xlab='Weight (kg)',yaxt='n',ylab='')
for(i in ind_model[-1]){
  ind = !is.infinite(log10(above_threshold[i, ]/100))
  lines(seq(40,90,by=5)[ind], log10(above_threshold[i,ind]/100),lwd=lwds[i],col=cols[i],lty=ltys[i])
}
axis(2, at = -3:0, labels = 10^(-3:0))
abline(h = -2, v=55, lty=2)
mtext(text = 'Probability Cmax > 1% threshold',side = 2,line = 4.5,las=3,cex=1.5)
mtext(text = 'B',side = 3,cex=1.5,adj = 0)


## Probability of being above threshold
plot(seq(40,90,by=5), mean_mortality_per_thousand[ind_model[1], ], type='l',main='',
     col=cols[ind_model[1]],lwd=lwds[ind_model[1]],xlab='Weight (kg)',ylab='',
     ylim=range(mean_mortality_per_thousand), panel.first = grid())
for(i in ind_model[-1]){
  lines(seq(40,90,by=5),  mean_mortality_per_thousand[i,],lwd=lwds[i],col=cols[i],lty=ltys[i])
}
legend('topright',col = cols[ind_model], title = 'Chloroquine regimen',
       legend = legend_names, lwd=lwds[ind_model], lty=ltys[ind_model])
mtext(text = 'Predicted mortality per thousand',side = 2,line = 4.5,las=3,cex=1.5)
mtext(text = 'C',side = 3,cex=1.5,adj = 0)
```


```{r Fig1, fig.width=9, fig.height=9}
x_points = c(1,3,10,20,100)

par(mfrow=c(2,1),las=1, cex.lab=1.5, cex.axis=1.5, family='serif',bty='n',mar=c(5,6,2,2))
hist(log10(pooled_data$CQumolL_Admission[pooled_data$Outcome==0]), xlim = log10(c(1,100)),
     main='', breaks = seq(-1.25,2.125,by=.25/2),ylab='',
     xaxt='n',
     xlab = expression(paste('Whole blood chloroquine+desethychloroquine concentration (',mu,'mol/L)')), 
     col=adjustcolor('blue',alpha.f = .5))
hist(log10(pooled_data$CQumolL_Admission[pooled_data$Outcome==1]), 
     breaks = seq(-1,2,by=.25/2), add=T, col=adjustcolor('red',alpha.f = .5))
mtext(text = 'Number of patients',side = 2,line = 4.5,las=3,cex=1.5)
legend('topleft',  fill=adjustcolor(c('blue','red'),alpha.f = .5),
       legend = c('Survivors','Fatal cases'),inset=0.02, cex=1.5, bty='n',title = 'Outcome')
axis(1, at=log10(x_points),labels = x_points)
axis(1, at = log10(tick_points), labels = NA, tick = T)

plot(xs, (colMeans(Pred_mortality)), type = 'l', ylim = c(0,1),lwd=3, 
     xlab = expression(paste('Whole blood chloroquine concentration (',mu,'mol/L)')), 
     xlim = log(c(1,100)),ylab = '',xaxt='n',panel.first = grid())
mtext(text = 'Probability of death',side = 2,line = 4.5,las=3,cex=1.5)
polygon(c(xs, rev(xs)), 
        (c(apply(Pred_mortality,2,quantile, probs=0.025),
                rev(apply(Pred_mortality,2,quantile, probs=0.975)))),
        col = adjustcolor('grey',alpha.f = .4),border = NA)
lines(xs, (colMeans(Pred_mortality)), lwd=3)
axis(1, at=log(x_points),labels = x_points)
axis(1, at = log(tick_points), labels = NA, tick = T)
for(i in ind_model){
  abline(v = log(quantile(Cmax_pop[i,ws,,2], probs = 0.99,na.rm=T)), col=cols[i],lwd=3,lty=ltys[i])
  print(quantile(Cmax_pop[i,6,,1], probs = 0.99,na.rm=T))
}
legend('topleft',legend = legend_names,col=cols[ind_model],lwd=2,inset=0.02,lty=ltys,
       title = paste('99 percentile of Cmax for',Weight_interested,'kg adult'))
qs=quantile(OnePercent, probs = c(0.025,0.975))
polygon(x = log(c(qs,rev(qs))), y = c(-9,-9,1,1), col = adjustcolor('red',alpha.f = .2),border = NA)
```

Mortality per thousand across the weight categories
```{r}
writeLines('Mean predicted mortality')
knitr::kable(round(mean_mortality_per_thousand,1))
writeLines('Upper 95 CI of predicted mortality')
knitr::kable(round(uCI_mortality_per_thousand,1))
writeLines('Lower 95 CI of predicted mortality')
knitr::kable(round(lCI_mortality_per_thousand,1))

writeLines('Proportion of Cmax above 10umol/L')
knitr::kable(round(100*apply(Cmax_pop[,,,1] > 10, c(1,2), mean),1))
```


## Supplementary: Plasma PK model predictionsm

```{r}
writeLines(sprintf('Using a blood to plasma ratio of %s', plasma_to_whole_blood_ratio))
```


Healthy volunteer model based on plasma measurements: predictions for Cmax greater than threshold and per thousand mortality
```{r S_Fig2, fig.width=10, fig.height=9}
# Set the indices to the simulations from the whole blood model
ind_model = ind_plasma

ltys = rep(c(1,1,1,2,2,1),2)
lwds = c(rep(3,6), rep(2,6))
tick_points = c(1:19,seq(20,100,by=10))
x_points = c(2,3,5,10,13,20)
legend_names = c('310mg daily (10 days)','600mg twice daily (10 days)',
                 '310mg daily (7 days)', 
                 'Weight-based (10 days)','Weight-based (7 days)',
                 'Malaria treatment (3 days)')
par(las=1, bty='n', family = 'serif',cex.lab=1.5, cex.axis=1.5,mar=c(5,6,2,2))
layout(mat = matrix(c(1,1,2,3), nrow = 2, byrow = T))

plot(density(log(Cmax_pop[ind_model[1],ws,,q]),na.rm=T), xlim = log(c(1, 20)),ylab='',yaxt='n', 
     xaxt='n', main='',col=cols[ind_model[1]],lwd=lwds[ind_model[1]], ylim=c(0,2.7),
     xlab = expression(paste('Whole blood chloroquine concentration (',mu,'mol/L)')))
for(i in ind_model[-1]){
  lines(density(log(Cmax_pop[i,ws,,q]),na.rm=T), lwd=lwds[i],col=cols[i],lty=ltys[i])
}
axis(1, at=log(x_points),labels = x_points)
axis(1, at = log(tick_points), labels = NA, tick = T)
legend('topleft',legend = legend_names,bg = 'white',col=cols[ind_model],
       lwd=2,inset=0.02,lty=ltys[ind_model],
       title = paste('Cmax for', Weight_interested,'kg adult'))
qs=quantile(OnePercent, probs = c(0.025,0.975))
polygon(x = log(c(qs,rev(qs))), y = c(-9,-9,10,10), 
        col = adjustcolor('red',alpha.f = .2),border = NA)
mtext(text = 'A',side = 3,cex=1.5,adj = 0)

## Probability of being above threshold
plot(seq(40,90,by=5), log10(above_threshold[ind_model[1], ]/100), type='l',main='',
     ylim=c(-3,0),col=cols[ind_model[1]],lwd=lwds[ind_model[1]],
     panel.first = grid(), xlab='Weight (kg)',yaxt='n',ylab='')
for(i in ind_model[-1]){
  ind = !is.infinite(log10(above_threshold[i, ]/100))
  lines(seq(40,90,by=5)[ind], log10(above_threshold[i,ind]/100),lwd=lwds[i],col=cols[i],lty=ltys[i])
}
axis(2, at = -3:0, labels = 10^(-3:0))
abline(h = -2, v=55, lty=2)
mtext(text = 'Probability Cmax > 1% threshold',side = 2,line = 4.5,las=3,cex=1.5)
mtext(text = 'B',side = 3,cex=1.5,adj = 0)


## Probability of being above threshold
plot(seq(40,90,by=5), mean_mortality_per_thousand[ind_model[1], ], type='l',main='',
     col=cols[ind_model[1]],lwd=lwds[ind_model[1]],xlab='Weight (kg)',ylab='',
     ylim=range(mean_mortality_per_thousand),panel.first = grid())
for(i in ind_model[-1]){
  lines(seq(40,90,by=5),  mean_mortality_per_thousand[i,],lwd=lwds[i],col=cols[i],lty=ltys[i])
}
legend('topright',col = cols[ind_model], title = 'Chloroquine regimen',
       legend = legend_names, lwd=lwds[ind_model], lty=ltys[ind_model])
mtext(text = 'Predicted mortality per thousand',side = 2,line = 4.5,las=3,cex=1.5)
mtext(text = 'C',side = 3,cex=1.5,adj = 0)
```


```{r S_Fig1, fig.width=9, fig.height=9}
x_points = c(1,3,10,20,100)

par(mfrow=c(2,1),las=1, cex.lab=1.5, cex.axis=1.5, family='serif',bty='n',mar=c(5,6,2,2))
hist(log10(pooled_data$CQumolL_Admission[pooled_data$Outcome==0]), xlim = log10(c(1,100)),
     main='', breaks = seq(-1.25,2.125,by=.25/2),ylab='',
     xaxt='n',
     xlab = expression(paste('Whole blood chloroquine+desethychloroquine concentration (',mu,'mol/L)')), 
     col=adjustcolor('blue',alpha.f = .5))
hist(log10(pooled_data$CQumolL_Admission[pooled_data$Outcome==1]), 
     breaks = seq(-1,2,by=.25/2), add=T, col=adjustcolor('red',alpha.f = .5))
mtext(text = 'Number of patients',side = 2,line = 4.5,las=3,cex=1.5)
legend('topleft',  fill=adjustcolor(c('blue','red'),alpha.f = .5),
       legend = c('Survivors','Fatal cases'),inset=0.02, cex=1.5, bty='n',title = 'Outcome')
axis(1, at=log10(x_points),labels = x_points)
axis(1, at = log10(tick_points), labels = NA, tick = T)

plot(xs, (colMeans(Pred_mortality)), type = 'l', ylim = c(0,1),lwd=3, 
     xlab = expression(paste('Whole blood chloroquine concentration (',mu,'mol/L)')), 
     xlim = log(c(1,100)),ylab = '',xaxt='n',panel.first = grid())
mtext(text = 'Probability of death',side = 2,line = 4.5,las=3,cex=1.5)
polygon(c(xs, rev(xs)), 
        (c(apply(Pred_mortality,2,quantile, probs=0.025),
                rev(apply(Pred_mortality,2,quantile, probs=0.975)))),
        col = adjustcolor('grey',alpha.f = .4),border = NA)
lines(xs, (colMeans(Pred_mortality)), lwd=3)
axis(1, at=log(x_points),labels = x_points)
axis(1, at = log(tick_points), labels = NA, tick = T)
for(i in ind_model){
  abline(v = log(quantile(Cmax_pop[i,ws,,2], probs = 0.99,na.rm=T)), col=cols[i],lwd=3,lty=ltys[i])
  print(quantile(Cmax_pop[i,6,,1], probs = 0.99,na.rm=T))
}
legend('topleft',legend = legend_names,col=cols[ind_model],lwd=2,inset=0.02,lty=ltys,
       title = paste('99 percentile of Cmax for', Weight_interested,'kg adult'))
qs=quantile(OnePercent, probs = c(0.025,0.975))
polygon(x = log(c(qs,rev(qs))), y = c(-9,-9,1,1), col = adjustcolor('red',alpha.f = .2),border = NA)
```